Differentiable Neural Computers

### 2018-05-04 Presentation/Presentation.tex
LSTM sketch

%----------------------------------------------------------------------------
% LoCo
%----------------------------------------------------------------------------
\setbeamertemplate{frametitle}[default][center]

@@

% Graphs
\usepackage{tikz}
\usetikzlibrary{calc, trees, fit}
\usepackage{pgfplots}
% Graphics
\usepackage{graphics}
\graphicspath{{figures/}} % Location of the graphics files

\newcommand\todo[1]{\textcolor{red}{#1}}
\newcommand{\w}[1]{\textit{"#1"}}
\newcommand{\sm}[1]{\text{\small{#1}}}
\newcommand\s{\textsc}

@@

\begin{frame}{Approach}
	Allow an RNN to act as a controller to interact with a memory matrix of N (arbitrary many) addresses.
	\pause
	\begin{enumerate}
	\item \alert{Content Lookup}\\
		\begin{itemize}
		\item \alert{Attention} over memory defined by weightings $W \in \mathbb{R}^N$
		\item Compare controller output with memory objects (\alert{auto-associative memory})
		\item Allow partial matches  (\alert{pattern completion})
		\end{itemize}
	\pause
	\item \alert{Sequential Retrieval}
		\begin{itemize} 
		\item Fill $L \in \{0,1\}^{2N}$ indexing \alert{temporal transitions}
		\item \alert{Shift} operations defined by $LW,\ L^TW$
		\end{itemize}
	\pause
	\item \alert{Dynamic Allocation}
		\begin{itemize}
		\item Mark memory locations with $\{0,1\}$ to \alert{signal usage}
		\item Manipulate signals during R/W operations to enable \alert{reallocation}
		\item Generalization to \alert{unbounded memory}
		\end{itemize}
	\end{enumerate}
\end{frame}

\begin{frame}{Controller}
A deep long-short term memory unit receiving 
\[
\pmb{\small{\mathcal{X}}}_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R]
\]
and producing
\[
\pmb{a}
\]
\end{frame}
\end{document}

>>>>

%----------------------------------------------------------------------------
% LoCo
%----------------------------------------------------------------------------
\setbeamertemplate{frametitle}[default][center]
\newcommand{\xx}{\pmb{\raisebox{-1.5pt}{$\mathcal{X}$}}}
\newcommand{\hh}{\pmb{h}}
\newcommand{\ii}{\pmb{i}}
\newcommand{\oo}{\pmb{o}}
\newcommand{\ff}{\pmb{f}}
\newcommand{\Ss}{\pmb{s}}
\newcommand{\bb}{\pmb{b}}

@@

% Graphs
\usepackage{tikz}
\usetikzlibrary{calc, trees, fit, positioning}
\usepackage{pgfplots}
% Graphics
\usepackage{graphics}
\graphicspath{{figures/}} % Location of the graphics files

\newcommand\todo[1]{\textcolor{red}{#1}}
\newcommand{\w}[1]{\textit{"#1"}}
\newcommand{\sm}[1]{\text{\small{#1}}}

@@

\begin{frame}{Approach}
	Train a RNN to act as a \alert{controller} to interact with a memory matrix of N (arbitrary many) addresses.
	\pause
	\begin{enumerate}
	\item \alert{Content Lookup}\\
		\begin{itemize}
		\item \alert{Attention} over memory defined by weightings $W \in \mathbb{R}^N$
		\item Compare controller output with memory objects (\alert{auto-associative memory})
		\item Allow partial matches  (\alert{pattern completion})
		\end{itemize}
	\pause
	\item \alert{Sequential Retrieval}
		\begin{itemize} 
		\item Fill $L \in \{0,1\}^{2N}$ indexing \alert{temporal transitions}
		\item \alert{Shift} operations defined by $LW,\ L^TW$
		\end{itemize}
	\pause
	\item \alert{Dynamic Allocation}
		\begin{itemize}
		\item Mark memory locations with $\{0,1\}$ to \alert{signal usage}
		\item Manipulate signals during R/W operations to enable \alert{reallocation}
		\item Generalization to \alert{unbounded memory}
		\end{itemize}
	\end{enumerate}
\end{frame}

\begin{frame}{Controller}
	A deep \alert{long short-term memory network} receiving 
	\[
	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R]
	\]
	and producing 
	\[
	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\theta)
	\]
	where $\mathcal{N}$ a set of state equations and $\theta$ their trainable parameters.
\end{frame}

\begin{frame}{Controller}
	A more detailed look into $\mathcal{N}$ and LSTMs:\\
	\begin{align}
	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
	\nonumber \\ 
	\pmb{v}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
	\end{align}
\end{frame}

\begin{frame}{Controller}
	\begin{figure}
	\begin{tikzpicture}[scale=0.5]
		% LSTM
		% outer box
		\draw[thick] (0,0) |- (18,12);
		\draw[thick] (18,12) |- (0,0);
		% core nodes
		\node (s) at (9,6) {$s$};
		\node (fx) at (9,4) {$x$};
		\node (f) at (9,2) {$f$};
		\node (i) at (6,8) {$i$};
		\node (ix) at (6,6) {$x$};
		\node (id) at (4,6) {$S$};
		\node (o) at (12,10) {$o$};
		\node (ox) at (16,6) {$x$};
		\node (od) at (12,6) {$S$};
		% recurrency
		\draw (f) -| (2,6);
		\draw (2,6) |- (o);
		% gates
		\draw (o) edge (ox);
		\draw (i) edge (ix);
		\draw (s) edge[bend right=90] (fx);
		\draw (s) edge[bend left=90] (fx);
		\draw (f) edge (fx);
		% forward
		\draw (0,6) edge (9,6);
		\draw (s) edge (od);
		\draw (od) edge (18,6);
		\end{tikzpicture}
	\end{figure}
\end{frame}
\end{document}
